\documentclass[12pt,a4paper]{article}
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
\usepackage{tgpagella}
\usepackage{hyperref}
\usepackage{microtype}
\hypersetup{colorlinks, breaklinks, urlcolor = Maroon, linkcolor = Maroon}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Aminreza Ghorbani}}

\vspace{0.4em}
+98 (912) 804-3895\ \ \textbullet
\ \ \href{mailto:aminreza369@gmail.com}{aminreza369@gmail.com}\ \ \textbullet \ \ 1990, May 30
\end{center}
\vspace{0.3em}

\hrule
\vspace{-0.4em}
\subsection*{Work Experience}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{Abdal Industrial Group (Mapsa)}}

	\\
	\headerrow
		{\emph{Designer, Rotary Equipments Department}}
		{\emph{2014 -- Present}}
	\begin{itemize*}
	    \itemsep0.15em
		\item Assisted reverse engineering of a Horizontal Centrifugal Process Pump.
		\item Assisted reverse engineering of a Barrel Casing Pump.
		\item Assisted reverse engineering of a Capillary Pressure Desaturator for the Core Analysis Laboratory.
		\item Designed medium-sized water storage tanks.
	\end{itemize*}
\vspace{-0.3em}
Reference: M. Hashemi\ \ $\cdotp$\ \ +98 (912) 388 9655\ \ $\cdotp$\ \ \href{mailto:h.hashemi@mapsaeng.com}{h.hashemi@mapsaeng.com}

	\item
	\headerrow
		{\textbf{Pars Petro Kupal Kish}}

	\\
	\headerrow
		{\emph{Project Planner, Project Control Department}}
		{\emph{2013 -- 2014}}
	\begin{itemize*}
		\item Assisted planning workover operations for Salman gas field wells.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{DRG Drilling Services}}

	\\
	\headerrow
		{\emph{Summer Intern, Drilling Department}}
		{\emph{2012}}
	\begin{itemize*}
		\item Examined different methods of directional \& horizontal drilling operations in South Pars gas field to achieve higher production rates.
	\end{itemize*}

\item
	\headerrow
		{\textbf{South Pars Oil \& Gas Co. (P.O.G.C)}}

	\\
	\headerrow
		{\emph{Summer Intern, Oil \& Gas Engineering Department}}
		{\emph{2011}}
	\begin{itemize*}
		\item Studied reservoir data of South Pars gas field including: main production parameters, locations of wells and phase production rates.
	\end{itemize*}

\item
	\headerrow
		{\textbf{Tehran Oil Refinery}}

	\\
	\headerrow
		{\emph{Summer Intern, Turbo-machinery Maintenance Workshop}}
		{\emph{2010}}
	\begin{itemize*}
		\item Assisted repair and maintenance of reciprocating pumps.
	\end{itemize*}
\end{itemize}
\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{University of Tehran}}
		{\textbf{Tehran}}
	\\
	\headerrow
		{\emph{Faculty of Mechanical Engineering, B.S. Mechanical Engineering}}
		{\emph{2008 -- 2013}}
	\begin{itemize*}
		\item Thesis title: ``Reverse engineering and dynamic simulation of a Synchro-Self-Shifting (SSS) clutch''\newline
		Adviser: A. Hannaneh
	\end{itemize*}

\end{itemize}
\newpage

\hrule
\vspace{-0.4em}
\subsection*{Computer Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
    \itemsep0.3em
	\item[Programming Languages:]
	\CPP, Python, Wolfram Language (Mathematica)
	\item[CAD:]
	AutoCAD, SolidWorks
	\item[Simulation \& Analysis:]
	ANSYS Workbench, PumpLinx
	\item[Project Management:]
	Microsoft Project
	\item[General Purpose:]
	\LaTeX, Microsoft Office
\end{description*}
\end{indentsection}

\hrule
\vspace{-0.4em}
\subsection*{Languages}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
    \itemsep0.3em
	\item[Persian:]
	Native
	\item[English:]
	Full professional proficiency
	\item[Arabic:]
	Elementary proficiency
\end{description*}
\end{indentsection}
\begin{flushright}
    \today
\end{flushright}

\end{document}
